X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt}

### 2013-09-04 natphys/hedpc_natphys.tex
Nature Physics guide compliance
    - caption, babel packages
    - FIG -> Figure
    - New abstract less than 150 words
    - Small changes to the introduction
    - no bibtex

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
%% for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}
% for double-spaced preprint
%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
%for review and submission
\documentclass[aps,prl,preprint]{revtex4-1} 
% for double-spaced preprint
%\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
%\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}

%% Packages
\usepackage[utf8]{inputenc} %Umlaute
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}

%% New commands
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}

@@

\author{T.~Thüring}
\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{M.~Abis}
\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{Z.~Wang}
\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\author{C.~David}
\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\author{M.~Stampanoni}
\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}

@@

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    Phase contrast imaging with X-rays provides access to
    complementary physical contrast mechanisms. Phase sensitive imaging in
    the diagnostic energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ is still largely unexplored, as the
    current methods typically entail severe technical challenges. A
    phase-contrast technique at such high energies is of scientific and
    industrial interest as it vastly expands the range of applications, for
    instance, by the examination of materials of high density or thickness.
    The approach includes a new design for the grating manufacturing in
    Talbot-Lau interferometry, with an edge-on illumination and curved
    structures to match the beam divergence. The edge-on approach breaks the
    current limits of achievable grating aspect ratios, which has been a key
    issue for a long time. The curvature of the gratings solves the
    intrinsic reduction of the field of view which occurs for gratings with
    such high aspect ratios and allows for a very compact setup, with a
    distance of \SI{31}{\centi\metre} between the source grating and the
    analyzer grating. Using an imaging arrangement based on a
    conventional X-ray tube, phase and dark-field contrast imaging at
    $\SI{100}{\kilo\electronvolt}$ is demonstrated. This achievement paves
    the road for the transfer of phase-contrast imaging into fields where
    high energies are required, such as medical computed tomography, chip
    failure analysis or homeland security.
\end{abstract}

@@

X-ray radiography and \ac{CT} are nowadays standard imaging techniques in
materials and life sciences for the nondestructive examination of samples or
the diagnosis of diseases in patients. The underlying contrast mechanism
relies on the different X-ray attenuation properties of different materials
or tissue types. The dominant physical effects contributing to attenuation
are the photoelectric effect and incoherent (Compton) scattering. The sum of
their contributions determines the attenuation coefficient, which is a
wavelength dependent material parameter. Besides attenuation, the wave
nature of X-rays reveals another contrast mechanism, which is the phase
shift. The interaction contributing to phase shifts is coherent (Rayleigh)
scattering \cite{Als-Nielsen2011}.

Using the material parameter $n=1-\delta(\mathbf{r},\lambda) + i
\beta(\mathbf{r},\lambda)$, known from X-ray wave optics as the complex
index of refraction, the wavelength dependent attenuation and phase shift
properties of an object at the spatial coordinate $\mathbf{r}$ are fully
described. The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the
attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi
\beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object
of thickness $d$ can be described by the line integral $L_\mu = \int_0^d
\mu(\mathbf{r},\lambda) \d l$. Similarly, the real part
$\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by
$\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi =
\int_0^d \phi(\mathbf{r}) \d l$.

While the attenuation line integral $L_\mu$ can be directly measured with an
X-ray detector by measuring the reduction of the beam intensity $I$ ($L_\mu
\propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is
more challenging as there is no such simple relation. However, phase
sensitive imaging is a desirable modality, as it can provide an enhanced
\ac{CNR} in images compared to attenuation for certain
materials or in different tissues \cite{Pfeiffer2007a,McDonald2009}.
Furthermore, the refractive index decrement $\delta$ provides direct access
to the electron density \cite{Als-Nielsen2011} and in combination with
attenuation, it further enables the determination of the effective atomic
number of a material \cite{Qi2010}.

In the past, a lot of effort has been invested into the development of
techniques which are sensitive to the phase shift. Since most of the
available phase contrast techniques rely on interference and thus typically
on optical hardware (e.g. crystals, gratings), they vary a lot in terms of
sensitivity, practical applicability or achievable resolution. The vast
majority of the methods, including crystal analyzer based
\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Techniques which are compatible with
an X-ray beam of low temporal coherence (broad bandwidth) are the in-line
phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded
apertures \cite{Munro2012}.

@@

\bibliographystyle{apsrev4-1} \bibliography{library}

>>>>

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
%% for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}
% for double-spaced preprint
%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
%for review and submission
\documentclass[aps,prl,preprint,english]{revtex4-1} 
% for double-spaced preprint
%\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
%\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}

%% Packages
\usepackage[utf8]{inputenc} %Umlaute
\usepackage{babel}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[bf,small,labelsep=period]{caption}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}

\addto\captionsenglish{\renewcommand{\figurename}{Figure}}
%% New commands
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}

@@

\author{T.~Thüring}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{M.~Abis}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{Z.~Wang}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\author{C.~David}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\author{M.~Stampanoni}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}

@@

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive to phase
    shifts, attenuation and scattering of the radiation.
    Applications of this technique in the diagnostically relevant energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due
    to the severe technical challenges.
    A phase-contrast technique at such high energies is of scientific and
    industrial interest for the analysis of materials of high atomic number or thickness
    as well as medical imaging.
    Here we show the design and operation of a Talbot-Lau
    interferometer with a target energy of $\SI{100}{\kilo\electronvolt}$ on
    a conventional X-ray tube and a compact geometry, with a total length of
    \SI{54}{\centi\metre}.
    The design features edge-on illumination in order to overcome the
    current limitations in the manufacturing of the gratings, and curved
    structures that match the beam divergence in order to allow for a large
    field of view and a short setup.
\end{abstract}

@@

X-ray radiography and \ac{CT} are standard imaging techniques in
materials and life sciences for the nondestructive examination of samples or
the diagnosis of diseases in patients. The underlying contrast mechanism
relies on the different X-ray attenuation properties of different materials
or tissue types. The dominant physical effects contributing to attenuation
are the photoelectric effect and incoherent (Compton) scattering. Besides attenuation, the wave
nature of X-rays reveals another contrast mechanism, which is the phase
shift. The interaction contributing to phase shifts is coherent (Rayleigh)
scattering \cite{Als-Nielsen2011}.

The attenuation and phase shift properties are described by the complex index of refraction
$n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$.
The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the
attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi
\beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object
of thickness $d$ can be described by the line integral $L_\mu = \int_0^d
\mu(\mathbf{r},\lambda) \d l$. Similarly, the real part
$\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by
$\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi =
\int_0^d \phi(\mathbf{r}) \d l$.

While the attenuation line integral $L_\mu$ can be directly measured with an
X-ray detector by measuring the reduction of the beam intensity $I$ ($L_\mu
\propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is
more challenging as there is no such simple relation. However, phase-sensitive
imaging is a desirable modality, as it can provide an enhanced
\ac{CNR} in images compared to attenuation for certain
materials or in different tissues \cite{Pfeiffer2007a,McDonald2009}.
Furthermore, the refractive index decrement $\delta$ provides direct access
to the electron density \cite{Als-Nielsen2011} and in combination with
attenuation, it further enables the determination of the effective atomic
number of a material \cite{Qi2010}.

In the past, a lot of effort has been invested into the development of
techniques which are sensitive to the phase shift. Since most of the
available phase contrast techniques rely on interference and thus typically
on optical hardware (e.g. crystals, gratings), they vary a lot in terms of
sensitivity, practical applicability or achievable resolution. The vast
majority of the methods, including crystal analyzer based
\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Techniques which are compatible with
an X-ray beam of low temporal coherence (broad bandwidth) are the inline
phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded
apertures \cite{Munro2012}.

@@

\bibliographystyle{apsrev4-1}

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (72) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{25}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Als-Nielsen}\ and\ \citenamefont
  {McMorrow}(2011)}]{Als-Nielsen2011}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Als-Nielsen}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {McMorrow}},\ }\href
  {http://books.google.com/books?hl=en\&lr=\&id=rlqlboWlTRMC\&oi=fnd\&pg=PA29\&dq=Elements+of+Modern+X-ray+Physics\&ots=P2D3XwrDgd\&sig=b3iO97q1hfsT8TkTYKxsvUbFink}
  {\emph {\bibinfo {title} {{Elements of modern X-ray physics}}}}\ (\bibinfo
  {year} {2011})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2007)\citenamefont
  {Pfeiffer}, \citenamefont {Bunk}, \citenamefont {David}, \citenamefont
  {Bech}, \citenamefont {{Le Duc}}, \citenamefont {Bravin},\ and\ \citenamefont
  {Cloetens}}]{Pfeiffer2007a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}},
  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Bech}}, \bibinfo {author}
  {\bibfnamefont {G.}~\bibnamefont {{Le Duc}}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Bravin}}, \ and\ \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Cloetens}},\ }\href {\doibase
  10.1088/0031-9155/52/23/010} {\bibfield  {journal} {\bibinfo  {journal}
  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {52}},\
  \bibinfo {pages} {6923} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {McDonald}\ \emph {et~al.}(2009)\citenamefont
  {McDonald}, \citenamefont {Marone}, \citenamefont {Hintermuller},
  \citenamefont {Mikuljan}, \citenamefont {David}, \citenamefont {Pfeiffer},
  \citenamefont {Stampanoni},\ and\ \citenamefont
  {Hinterm\"{u}ller}}]{McDonald2009}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
  {McDonald}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marone}},
  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Hintermuller}}, \bibinfo
  {author} {\bibfnamefont {G.}~\bibnamefont {Mikuljan}}, \bibinfo {author}
  {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo {author} {\bibfnamefont
  {F.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Stampanoni}}, \ and\ \bibinfo {author} {\bibfnamefont
  {C.}~\bibnamefont {Hinterm\"{u}ller}},\ }\href {\doibase
  10.1107/S0909049509017920} {\bibfield  {journal} {\bibinfo  {journal}
  {Journal of Synchrotron Radiation}\ }\textbf {\bibinfo {volume} {16}},\
  \bibinfo {pages} {562} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Qi}\ \emph {et~al.}(2010)\citenamefont {Qi},
  \citenamefont {Zambelli}, \citenamefont {Bevins},\ and\ \citenamefont
  {Chen}}]{Qi2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
  {Qi}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zambelli}},
  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Bevins}}, \ and\ \bibinfo
  {author} {\bibfnamefont {G.-H.}\ \bibnamefont {Chen}},\ }\href {\doibase
  10.1088/0031-9155/55/9/016} {\bibfield  {journal} {\bibinfo  {journal}
  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {55}},\
  \bibinfo {pages} {2669} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Davis}\ \emph {et~al.}(1995)\citenamefont {Davis},
  \citenamefont {Gao}, \citenamefont {Gureyev}, \citenamefont {Stevenson},\
  and\ \citenamefont {Wilkins}}]{Davis1995}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
  {Davis}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gao}}, \bibinfo
  {author} {\bibfnamefont {T.}~\bibnamefont {Gureyev}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Stevenson}}, \ and\ \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Wilkins}},\ }\href
  {http://imaging.sbes.vt.edu/laboratory/XGI/(1995 Gao).pdf} {\bibfield
  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {373}},\
  \bibinfo {pages} {595} (\bibinfo {year} {1995})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Chapman}\ \emph {et~al.}(1997)\citenamefont
  {Chapman}, \citenamefont {Thomlinson}, \citenamefont {Johnston},
  \citenamefont {Washburn}, \citenamefont {Pisano}, \citenamefont {Gm\"{u}r},
  \citenamefont {Zhong}, \citenamefont {Menk}, \citenamefont {Arfelli},\ and\
  \citenamefont {Sayers}}]{Chapman1997}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {Chapman}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Thomlinson}},
  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Johnston}}, \bibinfo
  {author} {\bibfnamefont {D.}~\bibnamefont {Washburn}}, \bibinfo {author}
  {\bibfnamefont {E.}~\bibnamefont {Pisano}}, \bibinfo {author} {\bibfnamefont
  {N.}~\bibnamefont {Gm\"{u}r}}, \bibinfo {author} {\bibfnamefont
  {Z.}~\bibnamefont {Zhong}}, \bibinfo {author} {\bibfnamefont
  {R.}~\bibnamefont {Menk}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Arfelli}}, \ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {Sayers}},\ }\href {\doibase 10.1016/j.carj.2010.04.015} {\bibfield
  {journal} {\bibinfo  {journal} {Physics in Medicine and Biology}\ }\textbf
  {\bibinfo {volume} {42}},\ \bibinfo {pages} {2015} (\bibinfo {year}
  {1997})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bonse}\ and\ \citenamefont {Hart}(1965)}]{Bonse1965}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
  {Bonse}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Hart}},\
  }\href {http://link.aip.org/link/?APPLAB/6/155/1} {\bibfield  {journal}
  {\bibinfo  {journal} {Applied Physics Letters}\ }\textbf {\bibinfo {volume}
  {6}},\ \bibinfo {pages} {155} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Momose}\ \emph {et~al.}(1996)\citenamefont {Momose},
  \citenamefont {Takeda}, \citenamefont {Itai},\ and\ \citenamefont
  {Hirano}}]{Momose1996}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Momose}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Takeda}},
  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Itai}}, \ and\ \bibinfo
  {author} {\bibfnamefont {K.}~\bibnamefont {Hirano}},\ }\href
  {http://imaging.sbes.vt.edu/laboratory/XGI/(1996 Momose).pdf} {\bibfield
  {journal} {\bibinfo  {journal} {Nature Medicine}\ }\textbf {\bibinfo {volume}
  {2}},\ \bibinfo {pages} {473} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Snigirev}\ \emph {et~al.}(1995)\citenamefont
  {Snigirev}, \citenamefont {Snigireva}, \citenamefont {Kohn}, \citenamefont
  {Kuznetsov},\ and\ \citenamefont {Schelokov}}]{Snigirev1995}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Snigirev}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Snigireva}},
  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Kohn}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Kuznetsov}}, \ and\ \bibinfo {author}
  {\bibfnamefont {I.}~\bibnamefont {Schelokov}},\ }\href
  {http://kohnvict.narod.ru/articles/091.pdf} {\bibfield  {journal} {\bibinfo
  {journal} {Review of Scientific Instruments}\ }\textbf {\bibinfo {volume}
  {66}},\ \bibinfo {pages} {5486} (\bibinfo {year} {1995})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Wilkins}\ \emph {et~al.}(1996)\citenamefont
  {Wilkins}, \citenamefont {Gureyev}, \citenamefont {Gao}, \citenamefont
  {Pogany},\ and\ \citenamefont {Stevenson}}]{Wilkins1996}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Wilkins}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Gureyev}},
  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gao}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Pogany}}, \ and\ \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Stevenson}},\ }\href
  {http://fisica.ufpr.br/lorxi/Rcf2/artigos/Wilkins.pdf} {\bibfield  {journal}
  {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {384}},\ \bibinfo
  {pages} {335} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Cloetens}\ \emph {et~al.}(1996)\citenamefont
  {Cloetens}, \citenamefont {Barrett}, \citenamefont {Baruchel}, \citenamefont
  {Guigay},\ and\ \citenamefont {Schlenker}}]{Cloetens1996}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Cloetens}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Barrett}},
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Baruchel}}, \bibinfo
  {author} {\bibfnamefont {J.}~\bibnamefont {Guigay}}, \ and\ \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Schlenker}},\ }\href
  {http://iopscience.iop.org/0022-3727/29/1/023} {\bibfield  {journal}
  {\bibinfo  {journal} {Journal of Physics D: Applied Physics}\ }\textbf
  {\bibinfo {volume} {29}},\ \bibinfo {pages} {133} (\bibinfo {year}
  {1996})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Cloetens}\ \emph {et~al.}(1997)\citenamefont
  {Cloetens}, \citenamefont {Guigay}, \citenamefont {{De Martino}},
  \citenamefont {Baruchel},\ and\ \citenamefont {Schlenker}}]{Cloetens1997}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Cloetens}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Guigay}},
  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {{De Martino}}}, \bibinfo
  {author} {\bibfnamefont {J.}~\bibnamefont {Baruchel}}, \ and\ \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Schlenker}},\ }\href
  {http://www.ncbi.nlm.nih.gov/pubmed/18185750} {\bibfield  {journal} {\bibinfo
   {journal} {Optics letters}\ }\textbf {\bibinfo {volume} {22}},\ \bibinfo
  {pages} {1059} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {David}\ \emph {et~al.}(2002)\citenamefont {David},
  \citenamefont {N\"{o}hammer}, \citenamefont {Solak},\ and\ \citenamefont
  {Ziegler}}]{David2002}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {David}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {N\"{o}hammer}},
  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Solak}}, \ and\ \bibinfo
  {author} {\bibfnamefont {E.}~\bibnamefont {Ziegler}},\ }\href {\doibase
  10.1063/1.1516611} {\bibfield  {journal} {\bibinfo  {journal} {Applied
  Physics Letters}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo {pages} {3287}
  (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Momose}\ \emph {et~al.}(2003)\citenamefont {Momose},
  \citenamefont {Kawamoto}, \citenamefont {Koyama}, \citenamefont {Hamaishi},
  \citenamefont {Takai},\ and\ \citenamefont {Suzuki}}]{Momose2003a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Momose}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kawamoto}},
  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Koyama}}, \bibinfo
  {author} {\bibfnamefont {Y.}~\bibnamefont {Hamaishi}}, \bibinfo {author}
  {\bibfnamefont {K.}~\bibnamefont {Takai}}, \ and\ \bibinfo {author}
  {\bibfnamefont {Y.}~\bibnamefont {Suzuki}},\ }\href {\doibase
  10.1143/JJAP.42.L866} {\bibfield  {journal} {\bibinfo  {journal} {Japanese
  Journal of Applied Physics}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo
  {pages} {L866} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2006)\citenamefont
  {Pfeiffer}, \citenamefont {Weitkamp}, \citenamefont {Bunk},\ and\
  \citenamefont {David}}]{Pfeiffer2006}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}},
  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \ and\ \bibinfo
  {author} {\bibfnamefont {C.}~\bibnamefont {David}},\ }\href {\doibase
  10.1038/nphys265} {\bibfield  {journal} {\bibinfo  {journal} {Nature
  Physics}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {258} (\bibinfo
  {year} {2006})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Munro}\ \emph {et~al.}(2012)\citenamefont {Munro},
  \citenamefont {Ignatyev}, \citenamefont {Speller},\ and\ \citenamefont
  {Olivo}}]{Munro2012}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Munro}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ignatyev}},
  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Speller}}, \ and\
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Olivo}},\ }\href
  {\doibase 10.1073/pnas.1205396109} {\bibfield  {journal} {\bibinfo  {journal}
  {Proceedings of the National Academy of Sciences}\ }\textbf {\bibinfo
  {volume} {2012}},\ \bibinfo {pages} {2} (\bibinfo {year} {2012})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Willner}\ \emph {et~al.}(2013)\citenamefont
  {Willner}, \citenamefont {Bech}, \citenamefont {Herzen}, \citenamefont
  {Zanette}, \citenamefont {Hahn}, \citenamefont {Kenntner}, \citenamefont
  {Mohr}, \citenamefont {Rack}, \citenamefont {Weitkamp},\ and\ \citenamefont
  {Pfeiffer}}]{Willner2013}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Willner}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bech}},
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Herzen}}, \bibinfo
  {author} {\bibfnamefont {I.}~\bibnamefont {Zanette}}, \bibinfo {author}
  {\bibfnamefont {D.}~\bibnamefont {Hahn}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Kenntner}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Rack}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}}, \
  and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}},\ }\href
  {http://www.ncbi.nlm.nih.gov/pubmed/23481949} {\bibfield  {journal} {\bibinfo
   {journal} {Optics express}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo
  {pages} {4155} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Ruiz}\ \emph {et~al.}(2013)\citenamefont {Ruiz},
  \citenamefont {Zanette}, \citenamefont {Chabior}, \citenamefont {Scherer},
